Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-05-04 paper.tex
Update values for nodes in Table 1

    Nodes & & 1,453,347 & & 783,231  & \\
    & Samples & 1,265,685 & (87\%) & 657,239 & (84\%) \\
    & Local (UPGMA) & 103K & (7.1\%) & 52K & (6.6\%)  \\
    & Tree adjustment & 80,830 & (5.6\%) & 72,107 & (9.2\%) \\
    & Recombination & 4,123 & (0.33\%) & 2,078 & (0.27\%) \\
    \cmidrule{2-6}
    % TODO add more information on mutations
    Mutations & & 1.21M &  & 1.06M & \\
    & On one sample & 759K & (63\%) & 767K & (72\%) \\
    & Reversions & 72K & (5.98\%) & 48K & (4.54\%) \\
    & per node & 0.83  &   & 1.36 \\
    \cmidrule{2-6}
    Recombination events & \\
    & Total & 4,123 & & 2,078 & \\
    & Singletons & 2,601  & (63\%) & 1,315 & (63\%) \\
    % clearer for many than "local trees?"
    & Unique breakpoints & 1,496 &  & 958 & \\
    \cmidrule{2-6}
    \multicolumn{2}{l}{Size (inc metadata)} & 57MB & & 36MB&  \\
    \multicolumn{2}{l}{Bytes/sample (exc metadata)}  & 8.29  & & 10.83 \\
    Load time & & 0.9s & & 0.5s & \\
    \bottomrule
\end{tabular}
\end{center}

@@

\subsubsection{Multiple origins} The ARG inference has no pre-defined knowledge
of Pango X lineage assignments, and there is therefore no particular
requirement that all the samples assigned to a given lineage must trace back to
a single recombination event. In this section we examine the Pango X lineage
samples that are inferred to have multiple recombinant origins (i.e., trace
back to different recombination nodes in the ARG), but still form monophyletic
clades % is this the right term? descending from these nodes .

@@

Figure~\ref{fig:pango-simple-origin-graph}C shows a simple example, consisting of
the 4 samples labelled XD by Nextclade in the long ARG. The left hand subgraph
(the origin of three XD samples) has an earliest
sample with EPI\_ISL: 11222324 (dated 2022-02-26), while the right hand
subgraph has a single sample with EPI\_ISL 8514045 (dated 2021-12-30). These
two samples differ by 35 mutations; considering this, and the time between the samples,
it does seem possible that they represent true independent origins of XD.
Supplementary Figure~\ref{fig:pango_XD_gisaid_graph} shows the same subgraphs
with sample identifiers and coloured by GISAID Pango labels (however, no
samples are designated by GISAID as XD in the long ARG).

Table \ref{tab:multiple_origins_table} summarises other Pango recombinants which
we infer to have multiple origins. [TODO: needs more detail]

@@

As well as cases where single recombination events explain an X lineage,
such as the examples in Figure~\ref{fig:pango-simple-origin-graph}, many of the
Pango X lineages involve more complex origins,
in which additional recombination events are nested inside the earliest shared
recombination. Frequently, the descendants of the original recombination
also include samples which have not been previously identified as recombinants.
An example is XB in the long ARG,
plotted in Figure~\ref{fig:complex_origins_graph}. Here, a recombination
between a B.1 sample and B.1.627 sample leads both to the XB samples and to a
``hairball'' of further recombination nodes whose descendants are mostly not
identified as recombinants by Nextclade, and plotted in blue. A similar
pattern is seen when examining XB in the wide ARG (discussion above, plot not shown).
Note that the descendants of nested recombination events include only one
XB sample (pink upper left, with 7 mutations above it); moreover, this sample is
not identified as XB by GISAID (Supplementary Figure~\ref{fig:pango_XB_gisaid_graph})
indicating some uncertainty in lineage assignment in this part of the ARG.
Investigating examples of complex recombinant origins, and identifying which
(if any) of the nested recombination events may be artifactual, is an important
area of future research.

@@

\subsection{The Li and Stephens model}
\label{sec:ls}
The Li and Stephens (LS) model\citep{Li2003-ib}  is an approximation of the
coalescent with recombination~\citep{Hudson1983-properties}, which captures
many of the important features of the joint processes of mutation and
recombination. It is a Hidden Markov Model (HMM) in which a focal genome is a
sequence of nucleotides that are probabilistically emitted as
an imperfect mosaic of a set of reference genomes
(Figure~\ref{fig:ls_diagram}).
The LS model is used in a wide variety
of applications in genomics, including modern approaches to
statistical genotype phasing and imputation
\citep{Delaneau2019-wl,Browning2021-cg,Browning2018-nk,Rubinacci2020-pa},
and estimation of parameters such as
recombination rates \citep[e.g.][]{Hinch2011-tz},
and selection within and across hosts in viral
sequence data \citep[e.g.][]{Palmer2019-wa}.
See~\cite{Mcvean2019-linkage} for further review and discussion
of the LS model.

@@

When the Viterbi algorithm implementation used by the LS HMM infers
recombinant ancestry for a given genome, the point at which inheritance
switches from one parent node to another is the last possible
position.
Thus, the breakpoints used in the ARG represent the rightmost end of the
interval, within which the recombination event could have occurred. To obtain
the leftmost end of this interval, we rerun the HMM using mirrored coordinates
(i.e., from the 3’ end to the 5’ end) and store the information as
metadata on the recombination node.
These left- and rightmost positions
are the recombination intervals reported throughout.
Ultimately all the recombination intervals mean is that the parent sequences
are identical within that interval, and there is therefore no information
about where the recombination occured. There are many different processes
that can contribute to the size of these intervals, and therefore
understanding how these processes interact to produce wider or narrower
intervals is an important avenue for future work.

@@

\renewcommand\thefigure{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand\thetable{S\arabic{table}}
\setcounter{table}{0}
\section*{Supplementary}
\subsection*{Supplementary methods}
\subsubsection*{Derivation of relation between recombination probability and mismatch probability conditional on mismatch ratio}
Without loss of generality, consider a region of length $m$. Up until this region, two paths are equally likely, so we can re-scale by the likelihood up to the site before the region starts.

@@

\begin{table}
% \begin{footnotesize}
\begin{tabular}{lllrl}
\toprule
lineage & ARG parents & Official Pango parents & n & Other descendants \\
\midrule
XA      &       B.1.1.7 + B.1.177.18 &     B.1.1.7 + B.1.177 &   5 & -- \\
XAA, XAG     &              BA.1 + BA.2.9 &         BA.1* + BA.2* &   8 &
    XAB: 39, XAG: 17, XAA: 8 \\
    &&&&   XAA: 8, XQ: 2, XU: ... \\
XAC     &          [BA.2.3, BA.1.17.2] &  [BA.2*, BA.1*, BA.2*] &  27 & -- \\
XAE     &                 [BA.2, BA.1] &         [BA.2*, BA.1*] &   9 & XAE: 9 \\
XAG     &               [BA.1, BA.2.9] &         [BA.1*, BA.2*] &  17 &
    XAB: 39, XAG: 17, XAA: 8 \\
    &&&&   XAA: 8, XQ: 2, XU: ... \\
XF      &                 [AY.4, BA.1] &    [B.1.617.2*, BA.1*] &   2 & XF: 2 \\
XG      &              [BA.1.17, BA.2] &         [BA.1*, BA.2*] &  32 & XG: 32, XAB: 1 \\
XH      &            [BA.1.20, BA.2.9] &         [BA.1*, BA.2*] &  11 &
    XAF: 34, XH: 11 \\
&&&& B.1.1.529: 3, XE: 3,... \\
XK      &             [BA.1.1.1, BA.2] &         [BA.1*, BA.2*] &   6 & XK: 3 \\
XL      &            [BA.1.17.2, BA.2] &         [BA.1*, BA.2*] &  10 &
    XL: 10, XAB: 1, XU: 1, \\
    &&&& XQ: 1 \\
XR      &               [BA.1.1, BA.2] &       [BA.1.1*, BA.2*] &   8 &
    XQ: 9, XR: 8, XAB: 2\\
XS      &              [AY.36, BA.1.1] &  [B.1.617.2*, BA.1.1*] &   6 & XS: 4\\
XT      &       [BA.2.23, Unknown (R)] &         [BA.2*, BA.1*] &   1 &
    BA.2: 1, BA.1: 1, BA.1.9: 1, \\
    &&&& BA.2.23:... \\
XV      &  [BA.1.1, BA.2, Unknown (R)] &         [BA.1*, BA.2*] &   3 & BA.2: 8, XV: 1 \\
XW      &            [BA.1.1.15, BA.2] &         [BA.1*, BA.2*] &  11 & XW: 11, XN: 2 \\
XY      &               [BA.1.1, BA.2] &         [BA.1*, BA.2*] &   6 & XY: 6, XAF: 1 \\
\bottomrule
\end{tabular}
\caption{\label{tab:pango-single-origin}
Summary of the Pango X-lineages in the long ARG that are inferred to have a single recombinant origin based on the NextClade Pango lineage assignments. Parent lineages from the ARG (as designated by Nextclade and, where relevant and also to parent lineages as defined by the official Pango designation alias key. (TODO: explain the asterisks) FIXME: if we like this table then we can reformat it so that lists at the end are spread over multiple lines rather than using Python dict notation }
\end{table}

\begin{figure} \centering
\includegraphics[width=0.5\textwidth]{figures/Pango_XA_gisaid_large_graph.pdf}
\caption{\label{fig:pango_XA_gisaid_graph}
Detailed version of Figure~\ref{fig:pango-simple-origin-graph}A. All single nucleotide mutations are listed
with the initial nucleotide state, followed by the reference genome position, followed by the derived
nucleotide state (after mutation). Sample nodes are shown with \emph{tskit} IDs, which can be mapped to
GISAID EPI ISL identifiers and strain names using supplementary file XXX. In contrast to
Figure~\ref{fig:pango-simple-origin-graph}A, Pango lineages shown here are those assigned by GISAID
rather than Nextclade. In the case of XA, Nextclade and GISAID agree completely on the lineage designations.
}
\end{figure}

\begin{sidewaysfigure} \centering
\includegraphics[width=\textwidth]{figures/Pango_XAG_gisaid_large_graph.pdf}
\caption{\label{fig:pango_XAG_gisaid_graph}
Detailed version of Figure~\ref{fig:pango-simple-origin-graph}B, with node and mutation labels as in
Figure~\ref{fig:pango_XA_gisaid_graph} (see supplementary file XXX to map tskID to EPI\_ISL and strain name).
Note that GISAID Pango designations assign an extra 2 samples to XAG, which are labelled as XAB
by Nextclade. This renders XAG fully monophyletic. However, unlike Nextclade, the GISAID designations
also mark many of the samples in this subgraph as non-recombinants (designating them BA.2), and in general
we find that Nextclade assignments agree more with our ARG structure than GISAID assignments.
}
\end{sidewaysfigure}

\begin{figure} \centering
\includegraphics[width=0.6\textwidth]{figures/Pango_XD_gisaid_large_graph.pdf}
\caption{\label{fig:pango_XD_gisaid_graph}
Detailed version of Figure~\ref{fig:pango-simple-origin-graph}C , with node and mutation labels as in
Figure~\ref{fig:pango_XA_gisaid_graph} (see supplementary file XXX to map tskID to EPI\_ISL and strain name).
Note that GISAID does not designate any nodes as XD in the long ARG, hence no recmbninant Pango designations
are marked in this plot. From inspection of the samples, we believe the GISAID designations to be erroneous
in this case.
}
\end{figure}

\begin{sidewaysfigure} \centering
\includegraphics[width=\textwidth]{figures/Pango_XB_gisaid_large_graph.pdf}
\caption{\label{fig:pango_XB_gisaid_graph}
Detailed version of Figure~\ref{fig:complex_origins_graph}, with node and mutation labels as in
Figure~\ref{fig:pango_XA_gisaid_graph} (see supplementary file XXX to map tskID to EPI\_ISL and strain name).
}
\end{sidewaysfigure}

>>>>

    Nodes & & 1,453,347 & & 783,231  & \\
    & Samples & 1,265,685 & (87.09\%) & 657,239 & (83.91\%) \\
    & Local (UPGMA) & 102,709 & (7.07\%) & 51,807 & (6.61\%)  \\
    & Reversion push & 40,538 & (2.79\%) & 34,358 & (4.39\%)  \\
    & Mutation collapse & 40,292 & (2.77\%) & 37,749 & (4.82\%)  \\
    & Recombination & 4,123 & (0.28\%) & 2,078 & (0.27\%) \\
    \cmidrule{2-6}
    % TODO add more information on mutations
    Mutations & & 1.21M &  & 1.06M & \\
    & On one sample & 759K & (63\%) & 767K & (72\%) \\
    & Reversions & 72K & (5.98\%) & 48K & (4.54\%) \\
    & per node & 0.83  &   & 1.36 \\
    \cmidrule{2-6}
    Recombination events & \\
    & Total & 4,123 & & 2,078 & \\
    & Singletons & 2,601  & (63\%) & 1,315 & (63\%) \\
    % clearer for many than "local trees?"
    & Unique breakpoints & 1,496 &  & 958 & \\
    \cmidrule{2-6}
    \multicolumn{2}{l}{Size (inc metadata)} & 57MB & & 36MB&  \\
    \multicolumn{2}{l}{Bytes/sample (exc metadata)}  & 8.29  & & 10.83 \\
    Load time & & 0.9s & & 0.5s & \\
    \bottomrule
\end{tabular}
\end{center}

@@

\subsubsection{Multiple origins} The ARG inference has no pre-defined knowledge
of Pango X lineage assignments, and there is therefore no particular
requirement that all the samples assigned to a given lineage must trace back to
a single recombination event. In this section we examine the Pango X lineage
samples that are inferred to have multiple recombinant origins (i.e., trace
back to independent recombination nodes in the ARG).

@@

Figure~\ref{fig:pango-simple-origin-graph}C shows a simple example, consisting of
the 4 samples labelled XD by Nextclade in the long ARG. The left hand subgraph
(the origin of three XD samples, all sampled in France) has an earliest
sample with EPI\_ISL: 11222324 (dated 2022-02-26), while the right hand
subgraph has a single sample with EPI\_ISL 8514045 (sampled in Turkey and dated 2021-12-30).
These two samples differ by 35 mutations; considering this, plus the geographical
locations and time between the samples,
it does seem possible that they represent true independent origins of XD.
Supplementary Figure~\ref{fig:pango_XD_gisaid_graph} shows the same subgraphs
with sample identifiers and coloured by GISAID Pango labels (however, no
samples are designated by GISAID as XD in the long ARG).

Another X lineage with multiple originating events is XE. In this case, however,
there are a large number of independent events. These

\ref{tab:multiple_origins_table} summarises other Pango recombinants which
we infer to have multiple origins. [TODO: needs more detail]
As with XD, none of the samples in the long ARG are identified as XE by GISAID.

@@

As well as cases where single recombination events explain an X lineage,
such as the examples in Figure~\ref{fig:pango-simple-origin-graph}, many of the
Pango X lineages involve more complex origins,
in which multiple non-independent (``nested'') recombination events are involved.
In these cases, the descendants of the original recombination
frequently include samples which have not been previously identified as recombinants.
An example is XB in the long ARG,
plotted in Figure~\ref{fig:complex_origins_graph}. Here, a recombination
between a B.1 sample and B.1.627 sample leads both to the XB samples and to a
``hairball'' of further recombination nodes whose descendants are mostly not
identified as recombinants by Nextclade, and plotted in blue. A similar
pattern is seen when examining XB in the wide ARG (discussion above, plot not shown).
Note that the descendants of nested recombination events include only one
XB sample (pink upper left, with 7 mutations above it); moreover, this sample is
not identified as XB by GISAID (Supplementary Figure~\ref{fig:pango_XB_gisaid_graph})
indicating some uncertainty in lineage assignment in this part of the ARG.
Investigating examples of complex recombinant origins, and identifying which
(if any) of the nested recombination events may be artefactual, is an important
area of future research.

@@

\subsection{The Li and Stephens model}
\label{sec:ls}
The Li and Stephens (LS) model \citep{Li2003-ib}  is an approximation of the
coalescent with recombination~\citep{Hudson1983-properties}, which captures
many of the important features of the joint processes of mutation and
recombination. It is a Hidden Markov Model (HMM) in which a focal genome is a
sequence of nucleotides that are probabilistically emitted as
an imperfect mosaic of a set of reference genomes
(Figure~\ref{fig:ls_diagram}).
The LS model is used in a wide variety
of applications in genomics, including modern approaches to
statistical genotype phasing and imputation
\citep{Delaneau2019-wl,Browning2021-cg,Browning2018-nk,Rubinacci2020-pa},
and estimation of parameters such as
recombination rates \citep[e.g.][]{Hinch2011-tz},
and selection within and across hosts in viral
sequence data \citep[e.g.][]{Palmer2019-wa}.
See~\cite{Mcvean2019-linkage} for further review and discussion
of the LS model.

@@

When the Viterbi algorithm implementation used by the LS HMM infers
recombinant ancestry for a given genome, the point at which inheritance
switches from one parent node to another is the last possible
position.
Thus, the breakpoints used in the ARG represent the rightmost end of the
interval, within which the recombination event could have occurred. To obtain
the leftmost end of this interval, we rerun the HMM using mirrored coordinates
(i.e., from the 3’ end to the 5’ end) and store the information as
metadata on the recombination node.
These left- and rightmost positions
are the recombination intervals reported throughout.
Ultimately all the recombination intervals mean is that the parent sequences
are identical within that interval, and there is therefore no information
about where the recombination occurred. There are many different processes
that can contribute to the size of these intervals, and therefore
understanding how these processes interact to produce wider or narrower
intervals is an important avenue for future work.

@@

\renewcommand\thefigure{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand\thetable{S\arabic{table}}
\setcounter{table}{0}
\section*{Supplementary}
\subsection*{Supplementary methods}
\subsubsection*{Derivation of relation between recombination probability and mismatch probability conditional on mismatch ratio}
Without loss of generality, consider a region of length $m$. Up until this region, two paths are equally likely, so we can re-scale by the likelihood up to the site before the region starts, $c$.

@@

\begin{table}
% \begin{footnotesize}
%% FIXME - commas and braces are confusing - I suggest separating by "+". The code to
%% produce this table is in Pango-recombinant-analysis.ipynb
\begin{tabular}{lllrl}
\toprule
lineage & ARG parents & Official Pango parents & n & Other descendants \\
\midrule
XA      &       B.1.1.7 + B.1.177.18 &     B.1.1.7 + B.1.177 &   5 & -- \\
XAA, XAG     &              BA.1 + BA.2.9 &         BA.1* + BA.2* &   8 &
    XAB: 39, XAG: 17, XAA: 8 \\
    &&&&   XAA: 8, XQ: 2, XU: ... \\
XAC     &          [BA.2.3, BA.1.17.2] &  [BA.2*, BA.1*, BA.2*] &  27 & -- \\
XAE     &                 [BA.2, BA.1] &         [BA.2*, BA.1*] &   9 & XAE: 9 \\
XAG     &               [BA.1, BA.2.9] &         [BA.1*, BA.2*] &  17 &
    XAB: 39, XAG: 17, XAA: 8 \\
    &&&&   XAA: 8, XQ: 2, XU: ... \\
XF      &                 [AY.4, BA.1] &    [B.1.617.2*, BA.1*] &   2 & XF: 2 \\
XG      &              [BA.1.17, BA.2] &         [BA.1*, BA.2*] &  32 & XG: 32, XAB: 1 \\
XH      &            [BA.1.20, BA.2.9] &         [BA.1*, BA.2*] &  11 &
    XAF: 34, XH: 11 \\
&&&& B.1.1.529: 3, XE: 3,... \\
XK      &             [BA.1.1.1, BA.2] &         [BA.1*, BA.2*] &   6 & XK: 3 \\
XL      &            [BA.1.17.2, BA.2] &         [BA.1*, BA.2*] &  10 &
    XL: 10, XAB: 1, XU: 1, \\
    &&&& XQ: 1 \\
XR      &               [BA.1.1, BA.2] &       [BA.1.1*, BA.2*] &   8 &
    XQ: 9, XR: 8, XAB: 2\\
XS      &              [AY.36, BA.1.1] &  [B.1.617.2*, BA.1.1*] &   6 & XS: 4\\
XT      &       [BA.2.23, Unknown (R)] &         [BA.2*, BA.1*] &   1 &
    BA.2: 1, BA.1: 1, BA.1.9: 1, \\
    &&&& BA.2.23:... \\
XV      &  [BA.1.1, BA.2, Unknown (R)] &         [BA.1*, BA.2*] &   3 & BA.2: 8, XV: 1 \\
XW      &            [BA.1.1.15, BA.2] &         [BA.1*, BA.2*] &  11 & XW: 11, XN: 2 \\
XY      &               [BA.1.1, BA.2] &         [BA.1*, BA.2*] &   6 & XY: 6, XAF: 1 \\
\bottomrule
\end{tabular}
\caption{\label{tab:pango-single-origin}
Summary of the Pango X-lineages in the long ARG that are inferred to have a single recombinant origin based on the NextClade Pango lineage assignments. Parent lineages from the ARG (as designated by Nextclade and, where relevant and also to parent lineages as defined by the official Pango designation alias key. (TODO: explain the asterisks) FIXME: if we like this table then we can reformat it so that lists at the end are spread over multiple lines rather than using Python dict notation }
\end{table}

\begin{figure} \centering
\includegraphics[width=0.5\textwidth]{figures/Pango_XA_gisaid_large_graph.pdf}
\caption{\label{fig:pango_XA_gisaid_graph}
Detailed version of Figure~\ref{fig:pango-simple-origin-graph}A. All single nucleotide mutations are listed
with the initial nucleotide state, followed by the reference genome position, followed by the derived
nucleotide state (after mutation). If an ancestral (``parent'') mutation exists at the same site in the path
to the root, it is possible for a mutation to be a ``reversion'' to the initial state of the parent mutation:
such reversions are indicated by lowercase nucleotide letters. Sample nodes are shown with \emph{tskit} IDs,
which can be mapped to GISAID EPI ISL identifiers and strain names using supplementary file \protect\path{Pango_X_graph_sample_maps.txt}. In contrast to
Figure~\ref{fig:pango-simple-origin-graph}A, Pango lineages shown here are those assigned by GISAID rather
than Nextclade; however, in the specific case of XA, Nextclade and GISAID exactly agree on the lineage designations.
}
\end{figure}

\begin{sidewaysfigure} \centering
\includegraphics[width=\textwidth]{figures/Pango_XAG_gisaid_large_graph.pdf}
\caption{\label{fig:pango_XAG_gisaid_graph}
Detailed version of Figure~\ref{fig:pango-simple-origin-graph}B, with node and mutation labels as in
Figure~\ref{fig:pango_XA_gisaid_graph} (see supplementary file \protect\path{Pango_X_graph_sample_maps.txt}
to map tskID to EPI\_ISL and strain name).
Note that GISAID Pango designations assign an extra 2 samples to XAG, which are labelled as XAB
by Nextclade in Figure~\ref{fig:pango-simple-origin-graph}B. This renders XAG fully monophyletic.
However, unlike Nextclade, the GISAID designations also mark many of the samples in this subgraph
as non-recombinants (designating them BA.2), and in general we find that Nextclade assignments
agree more with our ARG structure than GISAID assignments.
}
\end{sidewaysfigure}

\begin{figure} \centering
\includegraphics[width=0.6\textwidth]{figures/Pango_XD_gisaid_large_graph.pdf}
\caption{\label{fig:pango_XD_gisaid_graph}
Detailed version of Figure~\ref{fig:pango-simple-origin-graph}C, with node and mutation labels as in
Figure~\ref{fig:pango_XA_gisaid_graph} (see supplementary file \protect\path{Pango_X_graph_sample_maps.txt}
to map tskID to EPI\_ISL and strain name).
Note that GISAID does not designate any nodes as XD in the long ARG, hence no recmbninant Pango designations
are marked in this plot. From inspection of the samples, we believe the GISAID designations to be erroneous
in this case.
}
\end{figure}

\begin{sidewaysfigure} \centering
\includegraphics[width=\textwidth]{figures/Pango_XB_gisaid_large_graph.pdf}
\caption{\label{fig:pango_XB_gisaid_graph}
Detailed version of Figure~\ref{fig:complex_origins_graph}, with node and mutation labels as in
Figure~\ref{fig:pango_XA_gisaid_graph} (see supplementary file \protect\path{Pango_X_graph_sample_maps.txt}
to map tskID to EPI\_ISL and strain name).
The GISAID XB designations agree with the Nextclade ones except in two cases: an unplotted
singleton recombinant nested within the main grouping, and the tsk285180 node marked BA.1 in this plot,
but which is labelled XB by Nextstrain.
}
\end{sidewaysfigure}

%% Could insert the Pango_X_graph_sample_maps.txt with something like this
%% but maybe best to leave it as a separate file?
%% \lstinputlisting[caption={XXX}]{data/Pango_X_graph_sample_maps.txt}
